Sampling Strategies in Decisions from Experience

### 2022-04-22 manuscript.Rmd
minor reviews

shorttitle        : |
  Sampling strategies

@@

header-includes:
   - |
    \usepackage[capposition=top]{floatrow}
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
---

>>>>

shorttitle        : "Sampling strategies"

@@

header-includes:
   - \usepackage[capposition=top]{floatrow}
---
